Convolutional equivalent layer for gravity data processing

### 2020-03-26 manuscript/figures.tex
include new figures and modifications in text

\plot{Figure6}{width=8cm}{
	{Application to synthetic data. 
	(a) Predicted data produced by the fast equivalent-layer technique \citep{siqueira-etal2017}. 
	(b) Residuals between the simulated (Figure \ref{fig:synthetic_data}) and 
	predicted (shown in a) data. The mean and standard deviation are $8.264 \times 10^{-7}$ and $0.0144$ mGal,
	respectively.}
	\label{fig:classic_fast_val}
}

\plot{Figure7}{width=8cm}{
	{Application to synthetic data. 
	(a) Predicted data produced by our method. 
	(b) Residuals between the simulated (Figure \ref{fig:synthetic_data}) and 
	predicted (shown in a) data. The mean and standard deviation are $8.264 \times 10^{-7}$ and $0.0144$ mGal,
	respectively.}
	\label{fig:bccb_fast_val}
}

\plot{Figure8}{width=13.5cm}{
	{Application to synthetic data. 
	Difference between the predicted data produced by the fast equivalent-layer technique 
	(Figure \ref{fig:classic_fast_val}a) and by our method (Figure \ref{fig:bccb_fast_val}a).}
	\label{fig:delta_comparison}
}

\plot{Figure9}{width=13.5cm}{
	{Application to synthetic data. 
	Difference between the estimated mass distribution within the equivalent layers produced by 
	the fast equivalent-layer technique (not shown) and by our method (not shown).}
	\label{fig:delta_rho}
}

\plot{Figure10}{width=5cm}{
	{Application to synthetic data. 
	The upward-continued gravity data obtained with (a) the fast equivalent-layer technique 
	\citep{siqueira-etal2017} and (b) our method. (c) Residuals between 
	panels a and b with mean $-5.938 \times 10^{-18}$ mGal and standard deviation $8.701 \times 10^{-18}$ mGal. 
	The total computation times spent by the fast equivalent-layer technique and our method 
	are $7.62026$ and $0.00834$ seconds, respectively.}
	\label{fig:upward_comparison}
}

\plot{Figure11}{width=5cm}{
	{Application to synthetic data. 
	The downward-continued gravity data obtained with (a) the fast equivalent-layer technique 
	\citep{siqueira-etal2017} and (b) our method. (c) Residuals between 
	panels a and b with mean $5.914 \times 10^{-18}$ mGal and standard deviation $9.014 \times 10^{-18}$ mGal. 
	The total computation times spent by the fast equivalent-layer technique and our method 
	are $7.59654$ and $0.00547$ seconds, respectively.}
	\label{fig:downward_comparison}
}

@@

\plot{Figure13}{width=8cm}{
	{Application to field data over the Caraj{\'a}s Province, Brazil. 
	(a) Predicted data produced by our method. (b) Residuals between the observed  
	(Figure \ref{fig:carajas_real_data}) and the predicted data (panel a), with mean 
	$0.000292$ mGal and standard deviation of $0.105$ mGal.}
	\label{fig:carajas_gz_predito_val}
}

>>>>

\plot{Figure678_r1}{width=6cm}{
	{Application to synthetic data. 
	(a) Residuals between the simulated data (Figure \ref{fig:synthetic_data}) and 
	predicted data produced by the fast equivalent-layer technique \citep{siqueira-etal2017}. 
	The mean and standard deviation are $8.264 \times 10^{-7}$ and $0.0144$ mGal, respectively.
	(b) Residuals between the simulated data (Figure \ref{fig:synthetic_data}) and 
	predicted data produced by our method. The mean and standard deviation are 
	$8.264 \times 10^{-7}$ and $0.0144$ mGal, respectively.
	(c) Difference between the predicted data produced by the fast equivalent-layer technique 
	and our method.}
	\label{fig:comparison_datafits}
}

\plot{Figure10_r1}{width=6cm}{
	{Application to synthetic data.
	(a) Gravity data produced by the synthetic sources at $z = -XXXX$ m.
	(b) Residuals between the simulated data shown in a and the upward-continued 
	gravity data obtained with the fast equivalent-layer technique (not shown), with 
	mean $XXXXXX$ mGal and standard deviation $XXXXXX$ mGal. 
	(c) Residuals between the simulated data shown in a and the upward-continued 
	gravity data obtained with our method (not shown), with mean $XXXXX$ mGal and 
	standard deviation $XXXXX$ mGal. 
	The total computation times spent by the fast equivalent-layer technique and 
	our method were $7.62026$ and $0.00834$ seconds, respectively.}
	\label{fig:upward_comparison}
}

\plot{Figure11_r1}{width=6cm}{
	{Application to synthetic data. 
	(a) Gravity data produced by the synthetic sources at $z = -XXXX$ m.
	(b) Residuals between the simulated data shown in a and the downward-continued 
	gravity data obtained with the fast equivalent-layer technique (not shown), with 
	mean $XXXXXX$ mGal and standard deviation $XXXXXX$ mGal. 
	(c) Residuals between the simulated data shown in a and the downward-continued 
	gravity data obtained with our method (not shown), with mean $XXXXX$ mGal and 
	standard deviation $XXXXX$ mGal. 
	The total computation times spent by the fast equivalent-layer technique and 
	our method were $7.59654$ and $0.00547$ seconds, respectively.}
	\label{fig:downward_comparison}
}

@@

\plot{Figure13_r1}{width=8cm}{
	{Application to field data over the Caraj{\'a}s Province, Brazil. 
	(a) Predicted data produced by our method. (b) Residuals between the observed  
	(Figure \ref{fig:carajas_real_data}) and the predicted data (panel a), with mean 
	$0.000292$ mGal and standard deviation of $0.105$ mGal.}
	\label{fig:carajas_gz_predito_val}
}

### 2020-03-26 manuscript/synthetic_data.tex
include new figures and modifications in text

Figures \ref{fig:classic_fast_val}a and \ref{fig:bccb_fast_val}a show the data fits 
obtained, respectively, by the fast equivalent-layer technique \citep{siqueira-etal2017} 
and by our method. The corresponding residuals (Figures \ref{fig:classic_fast_val}b 
and \ref{fig:bccb_fast_val}b), defined as the difference between the simulated (Figure \ref{fig:synthetic_data}) 
and predicted data (Figures \ref{fig:classic_fast_val}a and \ref{fig:bccb_fast_val}a) after $N^{it} = 23$ iterations, 
show means close to zero and standard deviations of $0.0144$ mGal, indicating that both methods produced virtually 
the same results.
This excellent agreement is confirmed by Figures \ref{fig:delta_comparison} and 
\ref{fig:delta_rho}. They show that there are virtually no differences between, respectively, 
the predicted data (Figures \ref{fig:classic_fast_val}b and \ref{fig:bccb_fast_val}b) and the 
estimated mass distributions within the equivalent layers (not shown) yielded by 
both methods.

We performed the upward and downward continuations of the simulated gravity data 
(Figure \ref{fig:synthetic_data}) by using the estimated equivalent layers.
The results show that the continued gravity data obtained by using the 
fast equivalent-layer (Figures \ref{fig:upward_comparison}a and \ref{fig:downward_comparison}a) 
are in close agreement with those produced by our method (Figures \ref{fig:upward_comparison}b and 
\ref{fig:downward_comparison}b). The residuals (Figures \ref{fig:upward_comparison}c and \ref{fig:downward_comparison}c)
quantify this agreement since their means and standard deviations are close to zero.

The continued gravity data obtained with both methods agree with the true ones (not shown).
The difference is that the computation time spent by our method is 
approximately $1\,500$ times smaller than that of the fast-equivalent-layer 
technique \citep{siqueira-etal2017}.

>>>>

Figures \ref{fig:comparison_datafits}a and \ref{fig:comparison_datafits}b show the data fits 
obtained, respectively, by the fast equivalent-layer technique \citep{siqueira-etal2017} 
and by our method. They represent the differences between the simulated data (Figure \ref{fig:synthetic_data}) and the predicted data produced by both methods 
(not shown) after $N^{it} = 23$ iterations. 
As we can see, both methods produced virtually the same results.
This excellent agreement is confirmed by Figure \ref{fig:comparison_datafits}c, which shows 
the differences between the predicted data produced by both methods.

We performed the upward and downward continuations of the simulated gravity data 
(Figure \ref{fig:synthetic_data}) by using the fast equivalent-layer technique 
and our method.
Figure \ref{fig:upward_comparison} shows that the upward-continued gravity data obtained 
by using both methods are in close agreement with those produced by the synthetic 
bodies at $z = XXXX$ m (Figure \ref{fig:upward_comparison}a).
As we can see in Figures \ref{fig:upward_comparison}b and \ref{fig:upward_comparison}c,
the residuals between the upward-continued and true data have their means and standard 
deviations close to zero. 
Figure \ref{fig:downward_comparison} shows similar results obtained by using both 
methods to compute downward continuation of gravity data.
It is important to stress that, although both methods are able to produce a reliable 
upward/downward continuation of gravity data, the computation time spent by our method 
is approximately $1\,500$ times smaller than that of the fast equivalent-layer 
technique \citep{siqueira-etal2017}.
